---
title: "01 Intro to the tidyverse"
author: "Youcef Hassab"
date: "2021-05"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Challenge 1.1

First part of the code, loading the libraries and reading the files, here is a glimpse of the resulting tables :
```{r}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----
# Challenge 1.1

# 1.0 Load libraries ----
library(tidyverse)
library(tibble)  
library(readr)     
library(dplyr)    
library(magrittr) 
library(tidyr)    
library(stringr)  
library(ggplot2)
library(lubridate)
library(readxl)
# 2.0 Importing Files ----
bikes_tbl      <- read_excel("/home/icareyus/R_datascience/ds_basics-Clap-Trap1/01_tidyverse_files/ds_data/01_bike_sales/01_raw_data/bikes.xlsx")

orderlines_tbl <- read_excel("/home/icareyus/R_datascience/ds_basics-Clap-Trap1/01_tidyverse_files/ds_data/01_bike_sales/01_raw_data/orderlines.xlsx")

bikeshops_tbl <- read_excel("/home/icareyus/R_datascience/ds_basics-Clap-Trap1/01_tidyverse_files/ds_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

# 3.0 Examining Data  ----
glimpse(orderlines_tbl)

```
The second part is the data wrangling part, to get the data ready for plotting, then the part with the data visualization. Here is the final plot:

```{r}
# 4.0 Joining Data ----
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))

# 5.0 Wrangling Data ----
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  # 5.1 Separate category name
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  # 5.2 Add the total price (price * quantity) 
  mutate(total.price = price * quantity) %>%
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  #rename columns to _
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

# 6.1 Sales by state ----

# Step 1 - Manipulate
sales_by_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns
  select(state, total_price) %>%
  
  # Grouping by state and summarizing sales
  group_by(state) %>% 
  summarize(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

# Step 2 - Visualize
sales_by_state_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x =state, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  
  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    subtitle = "NRW is leading!",
    x = "state", # Override defaults for x and y
    y = "Revenue"
  )
  
```

It looks a bit crowded on the website, the plot on my local computer looks way better !

# Challenge 1.2

same as in 1.1, first part of the code, loading the libraries and reading the files, here is a glimpse of the resulting tables :

```{r}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----
# Challenge 1.2

# 1.0 Load libraries ----
library(tidyverse)
library(tibble)  
library(readr)     
library(dplyr)    
library(magrittr) 
library(tidyr)    
library(stringr)  
library(ggplot2)
library(lubridate)
library(readxl)
# 2.0 Importing Files ----
bikes_tbl      <- read_excel("/home/icareyus/R_datascience/ds_basics-Clap-Trap1/01_tidyverse_files/ds_data/01_bike_sales/01_raw_data/bikes.xlsx")

orderlines_tbl <- read_excel("/home/icareyus/R_datascience/ds_basics-Clap-Trap1/01_tidyverse_files/ds_data/01_bike_sales/01_raw_data/orderlines.xlsx")

bikeshops_tbl <- read_excel("/home/icareyus/R_datascience/ds_basics-Clap-Trap1/01_tidyverse_files/ds_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
# 3.0 Examining Data  ----
glimpse(orderlines_tbl)
```
same as in 1.1, The second part is the data wrangling part, to get the data ready for plotting, then the part with the data visualization. Here is the final plot:

```{r}
# 4.0 Joining Data ----
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
# 5.0 Wrangling Data ----
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  # 5.1 Separate category name
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  # 5.2 Add the total price (price * quantity) 
  mutate(total.price = price * quantity) %>%
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  #rename columns to _
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

# 6.1 Sales by state and year ----

# Step 1 - Manipulate
sales_by_year_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  select(order_date, state, total_price) %>%
  mutate(year = year(order_date)) %>%
  
  # Group by and summarize year and main catgegory
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

# Step 2 - Visualize

sales_by_year_state_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + 
  
  # Facet
  facet_wrap(~ state) +
  
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and state",
    subtitle = "Hamburg has an upward trend",
    fill = "Main category" # Changes the legend name
  )
```

It looks a bit crowded on the website, the plot on my local computer looks way better !