---
title: "03 Data Wrangling"
date: "2021-05"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Challenge 3

These are the codes for the third challenge, the reduced data set has been used. In the first chunk, libraries are loaded and data is read from the files and setup for the rest of the tasks : 

```{r}
library(vroom)
library(dplyr)
library(tidyverse)
library(vroom)
library(data.table)
library(tictoc)

#patent
col_types <- list(
  id = col_character(),
  type = col_character(),
  number = col_character(),
  country = col_character(),
  date = col_date("%Y-%m-%d"),
  abstract = col_character(),
  title = col_character(),
  kind = col_character(),
  num_claims = col_double(),
  filename = col_character(),
  withdrawn = col_double()
)

patent_tbl <- vroom(
  file       = "patent.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)
#assignee
col_types_assignee <- list(
  id = col_character(),
  type = col_character(),
  name_first = col_character(),
  name_last = col_character(),
  organization = col_character()
)

assignee_tbl <- vroom(
  file       = "assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

col_types_patent_assignee <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_character()
)

patent_assignee_tbl <- vroom(
  file       = "patent_assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

col_types_uspc <- list(
  uuid = col_character(),
  patent_id = col_character(),
  mainclass_id = col_character(),
  subclass_id = col_character(),
  sequence = col_integer()
)

uspc_tbl <- vroom(
  file       = "uspc.tsv", 
  delim      = "\t", 
  col_types  = col_types_uspc,
  na         = c("", "NA", "NULL")
) 

setDT(patent_tbl)
setDT(assignee_tbl)
setDT(patent_assignee_tbl)
setDT(uspc_tbl)

```

## Which US company has the most patents? 

```{r}

setnames(assignee_tbl, "id", "assignee_id")
patent_data <- merge(x = patent_assignee_tbl, y = assignee_tbl, by = "assignee_id")
us_patents <- patent_data %>%
  filter(type == 2)%>%
  filter(!is.na(patent_id) || !is.na(organization)) %>%
  select(-type, -assignee_id)%>% 
  group_by(organization) %>%
  count(patent_id) %>%
  select(-patent_id)%>%
  summarise(total = sum(n))%>%
  arrange(desc(total))%>% 
  slice(1:10) 
us_patents
```
IBMC has the most patents in the US!

## What US company had the most patents granted in August 2014? 

```{r}

  tbl_august <- patent_tbl %>%   
    separate(col  = date,
             into = c("year", "month", "day"),
             sep  = "-", remove = TRUE) %>%
    mutate(month = as.numeric(month))%>%
    filter(month == 08)%>%
    select(-year, -day)
  setnames(tbl_august, "id", "patent_id")
  us_patents_august<- merge(x = tbl_august, y = patent_data, by = "patent_id")%>%
    filter(type == 2 & num_claims == 1)%>%
    filter(!is.na(patent_id) || !is.na(organization)) %>%
    select(organization, patent_id) %>%
    group_by(organization) %>%
    count(patent_id) %>%   
    summarise(total_patents = sum(n))%>%
    arrange(desc(total_patents)) %>% slice(1:10)  
  us_patents_august
```
Microsoft Company had the most patents granted in August 2014.

## What is the most innovative tech sector ?

```{r}
  organization_data <- merge(x = uspc_tbl, y = patent_data, by = "patent_id") %>%
    filter(!is.na(patent_id) || !is.na(organization))%>%
    group_by(organization) %>%
    arrange(desc(mainclass_id)) %>%
    count(patent_id) %>%
    select(-patent_id)%>%
    summarise(total_patents_wordwide = sum(n))%>%
    ungroup() %>%
    arrange(desc(total_patents_wordwide)) %>% slice(1:10)  
top10_worlwid_top5_upts_ <- organization_data %>% slice(1:5)  
  top10_worlwid_top5_upts_  
```
  